Reinforcement Learning in Network Defence/Control (WIP)

### 2018-04-06 interim-talk/interim-talk.tex
Almost done!

\begin{frame}{Introducing: Reinforcement Learning}
	\begin{itemize}
		\item Goal: train an agent to make optimal decisions based on observed state.
		\begin{itemize}
			\item Formally, maximise the \alert{expected discounted reward}\footcite{RL2E}.
		\end{itemize}

@@

\begin{frame}{Why have RL in networks?}
	Link to recent work in data-driven networking/optimisation?

	Link to that one GMM paper w/ RL communication.
\end{frame}

@@

\begin{frame}{MARL for DDoS prevention}
	Network Model

	Pushback

	Group reward functions etc.
\end{frame}

\begin{frame}{The case for finer granularity}
	\begin{columns}
	\begin{column}{0.45\linewidth}
		\begin{itemize}
			\item Reduced service guarantees by nature of \emph{pushback} model.
			\begin{itemize}
				\item \alert{Worse with good-faith TCP congestion avoidance}.
			\end{itemize}
			%This is exacerbated by TCP congestion avoidance---legit hosts will be punished far more severely, bad actors don't care!

@@

\begin{frame}{Attacks}
	Poisoning attacks---explain.

	Evasion attacks---yes. These are what are often known as `adversarial examples'!
\end{frame}

\begin{frame}{The capabilities of attackers}
	Evasion for \emph{polymorphic blending attacks} on past models are known \NP-Complete. ?? How do they differ from modern perturbations, which are solved by stochastic optimisation?

	We have empirically measured bounds on the effectiveness of poisoning attacks wrt.\ what percentage of inbound traffic they can control.

	We don't have results for this on e.g., Deep RL in the network.

	We also lack results on how/if evasion attacks can transfer for learners focused on non-stationarity/constant learning.
\end{frame}

>>>>

\begin{frame}{Introducing: Reinforcement Learning (RL)}
	\begin{itemize}
		\item Goal: train an agent to make optimal decisions based on observed state.
		\begin{itemize}
			\item Formally, maximise the \alert{expected discounted reward}\footcite{RL2E}.
		\end{itemize}

@@

\begin{frame}{Why have RL in networks?}
	%Link to recent work in data-driven networking/optimisation?
	%
	%Link to that one GMM paper w/ RL communication.

	\begin{itemize}
		\item \alert{Data-driven networking.} Effectively applied to intra-domain routing \footcite{DBLP:conf/hotnets/ValadarskySST17}, task allocation \footcite{DBLP:conf/hotnets/MaoAMK16} and more, each with general and domain-specific insights.

		\item \alert{In intrusion detectors?} Optimising information sharing in distributed statistical model training \footcite{DBLP:conf/paisi/XuSH07}.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Multiagent RL for DDoS prevention}
%	Network Model \footcite{DBLP:journals/eaai/MalialisK15}
%	
%	Pushback \footcite{DBLP:journals/ccr/MahajanBFIPS02a}
%	
%	Group reward functions etc.
%
%	Its weaknesses? Strong assumptions about what knowledge the learners really have...

	\begin{itemize}
		\item Reimplementing (and poking holes in) MARL\footcite{DBLP:journals/eaai/MalialisK15}.
		% How? Violation of ISP-like criterion,

		\item Network model
		\begin{itemize}
			\item Hosts have a fixed probability of being benign/malicious.
			\item $n$ hosts per learner, $i$ learners to a team, $j$ teams, one server.
			\item Per-team rewards: \alert{coordinated team learning}.
			\item Action: (per-timestep) choose $p$, s.t. each learner drops $p\%$ of external traffic.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Flaws/Risks of MARL?}	
	\begin{itemize}		
		\item Action mechanism is \emph{pushback}\footcite{DBLP:journals/ccr/MahajanBFIPS02a} (probabilistic packet drop).

		\item Strong assumptions on benign/malicious packet estimation quality. 
		\item Pushback is known to be flawed in practice.
		\item Rigid ISP-like network assumptions.
	\end{itemize}
\end{frame}

\begin{frame}{The case for finer granularity}
	\begin{columns}
	\begin{column}{0.45\linewidth}
		\begin{itemize}
			\item Learner/host ratio (action/host ratio) affects host QoS.

			\item Reduced service guarantees by nature of \emph{pushback} model.
			\begin{itemize}
				\item \alert{Worse with good-faith TCP congestion avoidance}.
			\end{itemize}
			%This is exacerbated by TCP congestion avoidance---legit hosts will be punished far more severely, bad actors don't care!

@@

\begin{frame}{Attacks}
	\begin{description}
		\item[Poisoning attacks] Affect the training of a continuously learning model (RL agents, collaborative learning).

		\item[Evasion attacks] Make data/state appear to be different. These are what are often known as \alert{adversarial examples}!
	\end{description}
\end{frame}

\begin{frame}{The capabilities of attackers}
	\begin{itemize}
		\item Evasion for \emph{polymorphic blending attacks} (i.e., evasion) on past models are known \NP-Complete\footcite{DBLP:conf/ccs/FoglaL06}.

		\item We have empirical bounds on the effectiveness of poisoning attacks wrt.\ what percentage of inbound traffic an attacker controls\footcite{DBLP:journals/jmlr/KloftL10}.

		\item Careless model exposure $\implies$ black-box model extraction\footcite{DBLP:conf/uss/TramerZJRR16} $\implies$ evasion\footcite{DBLP:conf/sp/Carlini017}.

		%\item Promising work on defences\footcite{DBLP:conf/acsac/CaoG17}.
	\end{itemize}
\end{frame}

\begin{frame}{Unknowns}
	\begin{itemize}
		\item We don't have results for poisoning on e.g., Deep RL in the network.

		\item We also lack results on how/if evasion attacks can transfer for learners focused on non-stationarity/constant learning.

	\end{itemize}
\end{frame}
